\documentclass[11pt, reqno]{article}

\usepackage{amsmath, amsthm, amssymb}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{mathrsfs}
\usepackage{fancyhdr}
\usepackage[bottom=0.75in, top=1in, left=0.5in, right=0.5in]{geometry}
\usepackage{array}   % for \newcolumntype macro
\newcolumntype{L}{>{$}l<{$}}

\theoremstyle{plain}
\newtheorem*{theorem}{Theorem}
\newtheorem*{proposition}{Proposition}
\newtheorem{exercise}{Exercise}
\newtheorem*{lemma}{Lemma}
\newtheorem*{corollary}{Corollary}

\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem*{example}{Example}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\renewcommand{\phi}{\varphi}
\renewcommand{\epsilon}{\varepsilon}
\renewcommand{\emptyset}{\varnothing}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\QQ}{\mathbb{Q}}

\DeclareMathOperator{\ima}{\text{im}}

\begin{document}

\topmargin=-40pt
\rhead{Henry Woodburn}
\lhead{Math 655}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\headsep}{20pt}
\thispagestyle{fancy}

{\Huge \bfseries \noindent Homework 3}

\begin{enumerate}
    \item[1.] Let $(X, \tau)$ be a compact topological space and $\phi: (X ,\tau) \rightarrow \RR$ a 
    lower semicontinuous function. 
    
    Let $a = \inf_{x \in X} \phi(x)$. For each $\lambda > a$, 
    define $U_\lambda = \phi^{-1}(\left(-\infty, \lambda\right])$. Then the sets $U_\lambda$ are non-increasing
    as $\lambda$ decreases to $a$, and each of them are closed sets by the lower semicontinuity of $\phi$.
    Moreover, for any finite set $\lambda_1 < \cdots < \lambda_n$, we have 
    \[
        \bigcap_{i = 1}^n U_{\lambda_i} = U_{\lambda_1} \neq \emptyset,
    \]
    since $\lambda_1 > a$ and by the definition of infimum. Then since $X$ is compact, we have 
    \[
        \bigcap_{\lambda > a} U_\lambda \neq \emptyset.
    \]
    Choosing some $x_0 \in \bigcap_{\lambda > a} U_\lambda = \phi^{-1}(\left(-\infty, a\right])$, we 
    have $\phi(x_0) = a$ and thus $\phi$ achieves its infimum at $x_0$.

    \item[2.] Let $(X, \|\cdot\|)$ be a normed space and let $\phi: X \rightarrow \RR$ be a convex, 
    lower semicontinuous function. We will show that $\phi$ is lower semicontinuous in the $\sigma(X, X^*)$ 
    topology on $X$. Since we have that $\phi^{-1}(\left(-\infty, a\right])$ is norm-closed 
    for any $a \in \RR$, we only need to show that these sets are convex, and then we can apply Mazur's
    theorem to deduce that they are $\sigma(X, X^*)$-closed as well. 

    Suppose $\phi^{-1}(\left(-\infty, a\right]) = A$ is not convex. Then there exist points $x_1, x_2 \in A$
    and $t \in (0,1)$ such that $x_t = tx_1 + (1-t)x_2 \notin A$. In particular, we have 
    $\phi(x_1), \phi(x_2) \leq a < \phi(x_t)$. Then since $\phi$ is convex, 
    \[
        a < \phi(x_t) \leq t\phi(x_1) + (1-t)\phi(x_2) \leq a,
    \]
    a contradiction. Then the sets $\phi^{-1}(\left(-\infty, a\right])$ are convex and thus weakly closed, 
    and $\phi$ is lower semicontinuous in the $\sigma(X, X^*)$ topology. 

    \item[3.] Let $X$ be a reflexive Banach space, and $C \subset X$ a closed, convex subset. Let 
    $\phi: C \rightarrow \RR$ be a convex, lower semicontinuous function such that 
    \[
        \lim_{x \in C, \|x\| \rightarrow \infty} \phi(x) = + \infty.
    \]
    Then we show that $\phi(x)$ achieves its infimum $a$ on $X$. 

    By (2.), we know that $\phi$ is lower semicontinuous in $\sigma(X, X^*)$ as well. Since $X$ is 
    reflexive, the unit ball is compact in $\sigma(X,X^*)$. Then in order to apply
    the result of (1.), we just need to show that for some $M > a$, the preimages 
    $\phi^{-1}(\left(-\infty, \lambda\right])$ are contained in some closed ball about $0 \in X$. 

    But by the limit condition for $\phi$, we have that for all $M > 0$, there exists $\epsilon > 0$ 
    such that $\|x\| > \epsilon$ implies $\phi(x) > M$. Thus if $\phi(x) < M$, it must be that 
    $\|x\| < \epsilon$. Fix some $M > a$. Then for every $a < \lambda < M$, we have $\phi^{-1}(\left(-\infty, \lambda\right])
    \subset B(0, \epsilon)$. We note that $B(0, \epsilon)$ is compact by reflexivity. Then 
    similar to (1.), there is some point $x_0 \in \phi^{-1}(\left(-\infty, a\right])$ and 
    $\phi(x_0) = a$. 
\end{enumerate}

\end{document}